Nail: A practical interface generator for data formats

### 2014-09-11 paper/osdi14/concl.tex
eval and concl nits

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software.

% The source code for our prototype of Nail is available at
% \url{https://github.com/jbangert/nail}.

>>>>

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
establishing a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software, available at
\url{https://github.com/jbangert/nail}.
